My title

### 2023-03-14 outputs/paper/paper.qmd
data cleaning and generate graph for income, race, sex, industry sector, employee status. Data cleaning for eduyear and income.

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 
# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
### Input data ###
income_sex_data_percentage<-read.csv(here::here("outputs/data/sex_income.csv"))
income_race_data_percentage<-read.csv(here::here("outputs/data/race_income.csv"))
income_employee_status_data_percentage<-read.csv(here::here("outputs/data/income_employee_status_data.csv"))
income_industry_sector_data_percentage<-read.csv(here::here("outputs/data/income_industry_sector_data.csv"))
income_science_course_data_percentage<-read.csv(here::here("outputs/data/income_science_course_data.csv"))
```

@@

# Data {#sec-data}
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Sex"

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 
# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
### Input data ###
income_percentage<-read.csv(here::here("outputs/data/income_3years.csv"))
income_sex_data_percentage<-read.csv(here::here("outputs/data/sex_income.csv"))
income_race_data_percentage<-read.csv(here::here("outputs/data/race_income.csv"))
income_employee_status_data_percentage<-read.csv(here::here("outputs/data/income_employee_status_data.csv"))
income_industry_sector_data_percentage<-read.csv(here::here("outputs/data/income_industry_sector_data.csv"))
income_science_course_data_percentage<-read.csv(here::here("outputs/data/income_science_course_data.csv"))
```

@@

# Data {#sec-data}
```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution from 2014 to 2018"

# Make sure the order of the income level is the order we wanted
income_label <- c("LT $1000", "$1000 TO 2999", "$3000 TO 3999", "$4000 TO 4999", "$5000 TO 5999", "$6000 TO 6999", "$7000 TO 7999", "$8000 TO 9999", "$10000 - 14999", "$15000 - 19999", "$20000 - 24999", "$25000 OR MORE")
income_percentage$Income <- 
  factor(income_percentage$Income, 
         levels = income_label)

# Manually set fill colors and labels
fill_colors <- c("2014" = "#6B5B95", "2016" = "#ADD8E6", "2018" =  "#F5E5C0")

ggplot(income_percentage, aes(x = Income, 
                              y = Number, 
                              fill = Year)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = fill_colors) +
  labs(x = "Income Level", y = "Total Number of People",
       title = "U.S. Income Distribution by Year") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%"), y = Number + 10), 
            position = position_stack(vjust = 0.5), size = 2) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
  ylim(0, 420)

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-raceincome
#| fig-cap: "U.S. Income Distribution by Sex"
